\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-10-18 paper/manuscript_new.tex
small update to new research design

\textbf{Current scripts:}

@@

\textbf{Current scripts}: cityCoordinates.R (scrapes city coordinates from Wikipedia), combineURLs.R (combines Census with GSA data)

@@

@@

\textbf{Current scripts}: All of the preprocessing from section \ref{preprocessing_conventional} to \ref{preprocessing_duplicates} is currently done in malletPreprocessing.R (which doesn't require mallet anymore, so it's a bit of a misnomer).

@@

@@

@@

\textbf{Current scripts}: exampleDocuments.R

@@

@@

\textbf{Current scripts}: svmSKLN.ipynb (Indiana), svmSKLNLA.ipynb (Louisiana), elasticNet.R (Indiana)

>>>>

\textbf{Current scripts:} scrapeLousianaWebsites.R, scrapeIndianaWebsites.R (gets URls from Wikipedia), Indiana.R, Louisiana.R (combine Wikipedia and GSA URLs)

@@

\textbf{Current scripts}: cityCoordinates.R (scrapes city coordinates from Wikipedia), mapIndiana.R, combineURLs.R (combines Census with GSA data)

@@

\textbf{Current scripts}: internetarchive\_webarchive.R

@@

\textbf{Current scripts}: All of the preprocessing from section \ref{preprocessing_conventional} to \ref{preprocessing_duplicates} is currently done in malletPreprocessing.R and malletPreprocessingLA.R (which doesn't require mallet anymore, so it's a bit of a misnomer).

@@

\textbf{Current scripts}: malletPreprocessing.R, malletPreprocessingLA.R, hunspellParallel.R

@@

\textbf{Current scripts}: malletPreprocessing.R, malletPreprocessingLA.R

@@

\textbf{Current scripts}: exampleDocuments.R, topicCoherence.R, topicCoherenceNew.R, topicCoherenceTop10Topics.R, ldatuning.R (optimal number of topics), malletAnalysis.R, malletAnalysisDocumentEntropy.R, malletAnalysisHeatmap.R, malletAnalysisLA.R, malletAnalysisPartisanTopWords.R, malletAnalysisPartisanTopWordsLA.R, malletAnalysisPartisanTopics.R, malletAnalysisPartisanTopicsLA.R, malletTestParameters.R, malletTopWords.R, malletTraining.R

@@

\textbf{Current scripts}: stmAnalysis.R

@@

\textbf{Current scripts}: svmSKLN.ipynb (Indiana), svmSKLNLA.ipynb (Louisiana), elasticNet.R (Indiana), elasticSKLN.ipynb (Indiana), predictPartisanDocuments.R, predictPartisanDocumentsMLR.R
